
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]


%-------------------------
% Custom commands

% Bold title: regular text
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\projectName}[1]{
  \item\small{
    \textbf{#1}
  }
}

% Regular text
\newcommand{\listItem}[1]{
  \item\small{
    {#1}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}


    %-----------------HEADING-----------------
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\Huge Madiyar Bolatov}
 & Email: \href{mailto:hi@madiyar.dev}{hi@madiyar.dev} \\

\textbf{\Large Frontend Developer}
 & Telegram: \href{https://t.me/kawaii_neko}{kawaii\_neko} \\

Almaty, KZ, 26 y.o. (1998)
 & LinkedIn: \href{https://linkedin.com/in/madiyarkz}{madiyarkz} \\

\href{https://madiyar.dev}{https://madiyar.dev}
 & GitHub: \href{https://github.com/madiyar}{madiyar} \\


    \end{tabular*}


  %-----------------EXPERIENCE-----------------
  \section{Experience}
    \resumeSubHeadingListStart

        \resumeSubheading
          {Jmart}{Almaty, KZ}
          {Frontend Developer}{Aug. 2022 - Present}
          \resumeItemListStart

    \projectName{Jmart (jmart.kz)}
    \resumeItem{Stack}{React, Next.js TypeScript, Redux (Toolkit, Saga, Reselect), Zustand, ChakraUI, Styled-Components, Webpack, Microbundle, Node (Express), Turborepo}
    \listItem{Maintained and developed an own custom SSR solution on Express and Node.js.}
\listItem{Contributed to the development of a UI library (pyatka-ui).}
\listItem{Developed and maintained a wrapper for our REST API services (pyatka-sdk).}
\listItem{Improved a website performance (Lighthouse, CSR, LCP). Search engine optimization (SEO): microdata, meta-tags, open-graph.}
\listItem{Added code-splitting to reduce bundle size and improve load time.}
\listItem{Added virtualization to the product list with infinite scrolling to ensure smooth page performance.}
\listItem{Participated in migrating the project from legacy (Webpack, React 17) to Next.js 14 and Turborepo.}
\listItem{Assisted with setting up the Dockerfile and build configuration.}
\listItem{Participated in architectural decision-making and technology selection.}


          \resumeItemListEnd

        \resumeSubheading
          {Alfa Bank Kazakhstan}{Almaty, KZ}
          {Frontend Developer}{May. 2021 - Jun. 2022}
          \resumeItemListStart

    \projectName{1. Electronic Document Management (EDM) System}
    \resumeItem{Stack}{React, Redux, Webpack, WebSocket}
    \listItem{Developed electronic document signing (EDS) using biometrics via facial recognition through a webcam.}
\listItem{Refactored legacy code, updated dependencies, and migrated the project from an old deprecated UI library to a new one.}
\listItem{Developed automation and digitalization solutions for the bank's internal document workflow and business processes previously handled on paper.}


    \projectName{2. Alpha Space (Enterprise Portal / Intranet)}
    \resumeItem{Stack}{React, TypeScript, Redux Toolkit, React Query, Tailwind CSS}
    \listItem{Developed an admin panel for managing news and banners with Editor.js.}
\listItem{Started project development from scratch.}


          \resumeItemListEnd

        \resumeSubheading
          {DAR.tech}{Almaty, KZ}
          {Software Engineer}{May. 2020 - May. 2021}
          \resumeItemListStart

    \projectName{DAR Management System (DMS)}
    \resumeItem{Stack}{React, Next.js, Redux Saga, Nivo charts, Jest, React Testing Library, Material UI}
    \listItem{Developed a tool (Researcher), to analyze and compare competitors' social media, websites, and apps (with Rival IQ and SimilarWeb integration).}
\listItem{Developed a tool (Ad-manager), to manage all company ads (Google Adsense, Facebook Ads) from one platform.}
\listItem{Wrote unit tests using Jest and React Testing Library.}


          \resumeItemListEnd


    \resumeSubHeadingListEnd


    %-----------------EDUCATION-----------------
    \section{Education}
      \resumeSubHeadingListStart

          \resumeSubheading
            {Satbayev University}{Almaty, KZ}
            {Bachelor of Computer Science: GPA: 3.3}{Aug. 2017 -- Jun. 2020}

      \resumeSubHeadingListEnd


    %-----------------PROGRAMMING SKILLS-----------------
    \section{Programming Skills}
    \resumeSubHeadingListStart

        \item{
          \textbf{Languages}{: HTML/CSS, JavaScript, TypeScript}
        }

        \item{
          \textbf{Technologies}{: React, Next.js, Redux (Toolkit, Saga), Tanstack Query, RTK Query, Tailwind CSS, styled-components, emotion, Material UI, Chakra UI, Ant design, Jest, Testing Library, Vite.js}
        }

    \resumeSubHeadingListEnd

    %-------------------------------------------
    \end{document}
